A Detection of the Environmental Dependence of the Stellar Halos of Massive Central Galaxies

### 2017-03-24 draft/ms_v7.tex
Close to finishe

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the masked $i$-band image of this galaxy with the isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}\sim 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while the difference can exceed 0.2 dex in some cases.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ (red lines).
          }
      \label{fig:smf1}
  \end{figure*}

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Massive Central Galaxies from Low and High Mass Halos}
    \label{ssec:mass_central}

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}),
    the massive galaxies in our sample live in halos that span a wide range of 
    \mhalo{}.
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.

    We match the \texttt{hscZ} sample with the massive central galaxies of 
    \redm{} clusters with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$,
    and find 164 matched galaxies at $0.3 \leq z \leq 0.5$.
    We will refer these \textbf{central galaxies in more massive halos} as the 
    \rbcg{} sample here.
    A small fraction of \redm{} centrals within the HSC footprints is missing  
    due to severe contamination from optical artifacts or bright stars.
    The median $\lambda$ of these clusters is $\sim 41$, corresponding to 
    halo mass of $M_{\mathrm{halo}}\sim 2.2\times 10^{14} h^{-1} M_{\odot}$.
    Among them, only 44 of \rbcg{} sample live in clusters with $\lambda \geq 50$
    ($M_{\mathrm{halo}} \sim 3.0\times 10^{14} h^{-1} M_{\odot}$), so the \rbcg{} sample is 
    not dominated by extremely massive clusters with \mhalo{}$>10^{15} M_{\odot}$. 
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    To select massive central galaxies in \logmh{}$<14.0$ halos, we identify and 
    remove all galaxies within a cylinder region around each of the central galaxy of 
    all \redm{} clusters.
    We choose to use the $R_{\mathrm{halo}}$ as the radius, and twice the uncertainty of the 
    photometric redshift error as the thickness of the cylinder. 
    We convert the $\lambda$ into $M_{\mathrm{halo}}$ using the calibration in 
    \citet{Simet2016}, then estimate the $R_{\mathrm{halo}}$ with the help of the 
    mass-concentration relation in \citet{Diemer2015}. 
    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, 
    and is enough to exclude cluster members.
    After removing galaxies in \redm{} clusters, the rest of the massive galaxies 
    in our sample should mainly be the central galaxies of halos with \logmh{}$<14.0$,
    and we will refer these \textbf{central galaxies in less massive halos} as the 
    \nbcg{} sample.
    We should note that the \nbcg{} sample at this stage spans a large range in 
    \mstar{}, and includes contaminations like massive satellites in \logmh{}$< 14.0$ 
    halos.  
    Therefore, after we update the total \mstar{} later, we only focus on the 
    \nbcg{} galaxies at very high-mass end (e.g.~\logms{}$ > 11.5$). 
    According to recent observation (e.g. \citealt{vanUitert2016}), we can neglect 
    satellite contamination at such high \mstar{} range. 
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
    % TODO: The actual number waits to be updated}

    % \alexie{This is a rather strange procedure, I think we need to change it 
    % (referee and readers will complain!). What we really want to do is to remove any
    % galaxies that have $r<R200$ in projection (from the galaxy with the highest value 
    % of Pcen) and remove galaxies within some deltaz of the cluster redshift. 
    % The cluster redshift is more well determined than the redshift estimate of any 
    % cluster member. 
    % In short, what we are doing here is cutting out a cylinder around the most likely 
    % BCG. The deltaz value can be motivated by the cluster redshift uncertainty from 
    % the redmapper papers. The only remaining question is then what radius to use around
    % clusters. To get that number here is what we need to do. 
    % 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value 
    % of M\mathrm{halo} (halo mass defined as 200 time background) to each cluster. 
    % 3) we then need to estimate the cluster radius R\mathrm{halo} (or R200b, same thing). 
    % To do this, we need to use a mass-concentration relation. 
    % I'm pretty sure there is an easy command to do this in Python using the python 
    % package "colossus" by bendikt diemer. 
    % Download it and see if you an get it to work. If it doesn't look obvious after
    % 30 min, I can do it on my end using my own code. But good for you to know how to 
    % do this. We can simply use the mass-concentration relation from Benedikts work. 
    % 4) Now for every cluster you have R\mathrm{halo}. And you define the low halo mass central
    % sample as ones that are not within any cylindar around any cluster. 
    % Sorry, I know this might mean re-doing everything.....let's discuss by Skype if 
    % this is a major issue.}
%% ------------------------------------------------------------------------------------ %%

@@

    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample of massive central 
    galaxies with reliable redshift information, and broadly separate them into two 
    groups with different \mhalo{}. 
    The following is a summary of our sample construction.

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality images and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: through matching the \texttt{hscPho} sample with 
            spectroscopic redshifts from surveys like SDSS/BOSS and GAMA, or accurate 
            red-sequence photometric redshift in the \redm{} catalog, we come up with 
            a large sample of bright galaxies with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 164 galaxies at 
            $0.3 \leq z \leq 0.5$ that are reliably identified as the central galaxies 
            in $\lambda > 30$ \redm{} clusters. 
            They represent the central galaxies in very massive halos 
            (\logmh{}$\geq 14.2$). 
        \item \nbcg{} sample: after excluding all the galaxies that are close to any 
            \redm{} clusters in both radial and redshift directions from the 
            \texttt{hscZ} sample, we have 14661 bright galaxies at 
            $0.3 \leq z \leq 0.5$.
            With the help of \mstar{} estimates via SED fitting (see Section 
            \ref{ssec:isedfit}), we consider the massive ones among them as the 
            central galaxies in halos with \logmh{}$<14.0$.  
    \end{itemize}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Measurements of 1-D Surface Brightness Profile}
    \label{sec:ellipse}

    To estimate the total luminosity of massive galaxies, and measure their 
    one-dimensional stellar mass density (\mden{}) profiles, we perform elliptical 
    isophotes fitting using the IRAF \texttt{Ellipse} algorithm (Jedrzejewski 1987).  
    Compared to the popular two-dimensional model fitting method, the isophote fitting
    approach is insensitive to the choice of model (e.g. de~Vaucouleurs or \ser{} 
    profile), the number of components, and the initial guesses of free parameters. 
    It is also less affected by the background subtraction uncertainty, which is 
    particularly important for the massive ellipticals in our sample.
    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
    as the de~Vaucouleurs model or a single \ser component model. 
    These models will fail to simultaneously capture the profile in both the inner and 
    the outer region and these models also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a}; \citealt{Huang2013b}), but they are still 
    sensitive to background subtraction and initial values of parameters. 
    For this paper, we opt to for the model-independent 1-D approach and we will only 
    study galaxies in the radial range where we are not sensitive to either the PSF 
    ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).

    We prepare large $i$-band cut-out images for each galaxy in our sample that extend 
    to at least 750 kpc in radius, along with the bad pixel mask, and the PSF model 
    reconstructed at the central coordinate. 
    These cut-outs include all visible light of the galaxy while leaving enough space 
    to evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background level than the images 
    in $z$ and Y bands that are supposed to be better tracers of \mden{}.

    For each cut-out, to avoid the ``over-deblending'' issue within the 
    \texttt{hscPipe}, we use customized procedures to detect and appropriately mask 
    out all objects around the massive galaxies.
    Meanwhile, the \texttt{hscPipe} tends to over-subtract background around bright
    objects, including some of the massive galaxies in our sample. 
    After aggressively masking out all objects (including the central massive 
    galaxy), we derive an empirical background correction with the help from 
    \texttt{SExtractor}.
    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
    following the methodology in \citep{Li2012}. 
    In short, we start with free centroid and shape (ellipticity and position angle) 
    for each isophote, then fix the best-estimated centroid and estimate the mean 
    ellipticity and position angles of all isophotes.  
    Finally, we extract a 1-D surface brightness profile along the major axis using 
    the mean ellipticity and position angle. 
    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, then integrate them to various radius to get the 
    luminosity within different physical apertures. 
    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z\sim0.2$ together with the 
    colored image and a subset of isophotes.

    After testing the above procedure with different mask sizes, different 
    \texttt{Ellipse} parameters, and with or without background correction, 
    we find that the 1-D surface brightness profile is reliable above 
    $>28.5$ \sb. 
    Beyond that, some of the profiles begin to show unphysical behaviors 
    (truncation or large fluctuations) due to uncertainties from background subtraction. 
    This conservative choice already enables us to measure the individual surface 
    brightness profile out to $100$ kpc. 
    For more details about the technical details of the \texttt{Ellipse} run, please 
    see Appendix~\ref{app:ellipse}.

    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method. 
    It affects $18/164$ of the \rbcg{} galaxies, and a smaller fraction of the \nbcg{} 
    ones. 
    It is worth noting that this excludes most major-merging massive galaxies. 
    We will come back to them in the future using 2-D modeling method.
%% ------------------------------------------------------------------------------------ %%

@@

    To convert luminosities into stellar mass, we assume that these massive galaxies 
    can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are mostly dominated by 
    old stellar populations and are known to have shallow color gradients. 
    We will further justify this point by measuring their average color profiles in 
    Section \ref{ssec:ell_color}.

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes. 
    Although \cmodel{} tends to underestimate the total flux for bright, extended 
    objects, it can still yield accurate \emph{average} color thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipeInPrep}).

    \texttt{iSEDFit} takes a simplified Bayesian approach. 
    In short, it first generates a large grid of SEDs from synthetic stellar population 
    models by drawing randomly from the prior distributions of relevant parameters 
    (e.g.\ age, metallicity, dust extinction, and star formation history).
    Based on these models, it uses the observed photometry and redshift to compute the 
    statistical likelihood, and generates the posterior probability distribution 
    functions (PDF) for each parameter.  
    To get the best estimate of a given parameter, \texttt{iSEDFit} ``integrates'' the 
    full PDF over all the other ``nuisance'' parameters.
    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
    marginalized PDF. 
    Please refer to \citet{Moustakas13} for technical details.

@@

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but does
    not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    Based on tests using synthetic objects, we find that the average accuracy of
    \cmodel{} for bright galaxy is roughly at the 1\% level in the $r$, $i$, $z$ bands, 
    and slightly worse in the $g$ and Y-band. 
    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, 
    images in $gY$ bands are shallower in depth and/or have higher background noise).  
    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms$\sim 11.5$. 
    Please see Appendix~\ref{app:sed} for more detailed discussions of the SED fitting
    results.  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
          \textbf{Left}: Median \mden{} profiles of galaxies in different \mtot{} bins:
      	  [11.4, 11.6] (short-dashed line), [11.6, 11.8] (solid line), and 
      	  [11.8, 12.0] (long-dashed line). 
      	  Here we combine the \rbcg{} and \nbcg{} samples, and we also show a random 
      	  subset of individual profiles in the background.
      	  The shaded region highlights the region that could be affected by PSF.
          Two vertical lines label the radius of 10 kpc (thin, dotted line) and
          100 kpc (thick, dash line). ~~~ 
          \textbf{Right}: comparison between the average \mden{} profiles with the ones 
          from previous observations and simulations, including: 
          1) average profile of massive elliptical galaxies at $z\sim 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) average profile of massive galaxies at $0.25 \leq z < 0.50$ observed by 
          \textit{HST} from \citet[][Red, long-dashed]{Patel2013} ;
          3) average radial stellar distributions in massive halos using simulation and 
          particle tagging method (\citealt{Cooper13}; Purple, short-dashed).
          }
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          Comparison of the \mden{} profiles for \mtot{}-matched 
          ($11.6<$\logmtot{}$<11.9$) and \minn{}-matched ($11.2<$\logminn{}$<11.6$) 
          samples of \rbcg{} (orange to red) and \nbcg{} (grey to black) galaxies.~~
          \textbf{Left} shows the results for the \mtot{}-matched samples.
          For details of the matching process, please see Appendix~\ref{app:match}.  
          On its upper panel, we show the \mden{} profile of each galaxy using very light 
          color in the background.  
          We highlight the median profile and its corresponding uncertainties using thick 
          solid line with darker color and shaded region. 
          Other formats are the same with Fig~\ref{fig:avg_prof}.
          Meanwhile, we highlight the difference between the median profiles and its 
          uncertainty on the bottom panel (brown solid line and shaded region).
          To test the significance of the differential profile, we perform statistical
          tests by comparing the median profiles of two random groups that are drawn 
          from the mixed sample, and have the same sizes with the matched \rbcg{} and
          \nbcg{} ones.
          Repeating this process many times, the median of these random differential 
          profiles (black solid line), the 1-$\sigma$ (dark-grey shaded region) and 
          3-$\sigma$ (light-grey shaded region) uncertainties are shown on the bottom 
          panel as well. 
          A darker vertical dash-line highlights the 100 kpc radius.~~
          \textbf{Right} shows the results for the \minn{}-matched samples. 
          The format is exactly the same with the left one, except that the darker 
          vertical dash-line now highlights the 10 kpc radius.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%     
    \subsection{Impact of Photometry on Stellar Mass and Stellar Mass Function}
    \label{ssec:s82}

    As mentioned above, different methods lead to different estimates of ``total'' 
    \mstar{} and impacts important statistics like the stellar mass function 
    (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2016a}).
    We highlight this in the left panel of Fig~\ref{fig:smf1} by plotting 
    the \mtot{} from 1-D analysis with the differences between \mtot{} and \mcmodel{}.
    Apparently, our careful 1-D approach recovers more flux in massive galaxies 
    than the \texttt{cModel} method. 
    More importantly, the average difference steadily increases with \mtot{}. 
    At \logms$>11.5$, the difference is often larger than 0.2 dex.  
    This difference relates to the intrinsic limitation of the \texttt{cModel} 
    method and also reflects the fact that more massive ETGs tend to have more 
    extended stellar mass distributions (e.g. \citealt{Graham2003}).

>>>>

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}\sim 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Massive Central Galaxies in Low and High Mass Halos}
    \label{ssec:mass_central}

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
    live in a fairly broad range of halos masses.
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.

    We match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
    galaxies at $0.3 \leq z \leq 0.5$.
    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
    $\sim 41$, corresponding to halo mass of 
    $M_{\mathrm{halo}}\sim 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
    ($M_{\mathrm{halo}} \sim 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    Out next goal is to construct a sample of central galaxies living in halos with 
    \logmh{}$<14.0$. 
    We first identify and remove all galaxies within a cylindrical region around all 
    \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the uncertainty of the photometric redshift error. 
    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
    \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
    cluster members.
    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$\leq 14.0$. 
    We will refer to this sample of \textbf{central galaxies in less massive halos}
    as the \nbcg{} sample.

    We note that at this stage, our \nbcg{} sample still contains galaxies with a 
    wide range of \mstar{} values. 
    Later on, once we have more accurate \mstar{} estimates, we will further limit this 
    sample to \logms{}$ > 11.5$. 
    At this very high mass end, and given that we have rejected satellites in \redm{} 
    clusters, any further satellite contamination can be safely neglected 
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
    % TODO: The actual number waits to be updated}

@@

@@

    Using $\sim 100$ deg$^2$ of HSC data, we select a large sample of massive central 
    galaxies with reliable redshift information, and broadly separate them two 
    categories based on $M_{\mathrm{halo}}$.

    The following is a summary of our sample construction.

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 164 galaxies at 
            $0.3 \leq z \leq 0.5$ that are the central galaxies 
            in $\lambda > 30$ \redm{} clusters. 
            They represent the central galaxies in very massive halos 
            (\logmh{}$\geq 14.2$). 
        \item \nbcg{} sample: after excluding all cluster members from the 
            \texttt{hscZ} sample, we have 14661 bright galaxies at 
            $0.3 \leq z \leq 0.5$. 
            After applying an additional \mstar{} cut (see Section 
            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
            halos with \logmh{}$<14.0$.  
    \end{itemize}

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Measurements of 1-D Surface Brightness Profiles}
    \label{sec:ellipse}

    Massive ETGs imaged at the depth of HSC are not well modeled by simple models such 
    as the de~Vaucouleurs model or a single \ser component model. 
    These models will fail to simultaneously capture the profile in both the inner and 
    the outer region and these models also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
    the number of components, initial guesses of parameters, and the internal 
    degeneracies among different parameters. 
    Background subtraction uncertainty can affect the 2-D model fitting dramatically, 
    especially for massive ETGs in our sample. 
    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and measure their one-dimensional profiles of stellar mass surface 
    density (\mden{}). 
    This 1-D method we adopt is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not sensitive 
    to either the PSF ($r<3-5$ kpc) or the background subtraction ($r>100$ kpc).

    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask, and the PSF model. 
    These cut-outs include all of the light of the galaxy and are large enough to 
    also evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and Y band images (although these in principle may be better tracers of \mden{}).

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, we 
    use a customized procedure to detect and appropriately mask out neighbouring 
    objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To correct for this over-subtraction, we first aggressively mask all objects 
    (including the central massive galaxy), and derive an empirical background 
    correction using \texttt{SExtractor}.
    Then, we run \texttt{Ellipse} on the background-corrected, masked cut-outs 
    following the methodology of \citep{Li2012}. 
    In short, we first fit each isophote using a free centroid and shape 
    (ellipticity and position angle). 
    We then fix the centroid (using the mean flux-weighted centroid) and estimate
    the mean ellipticity and position angles of all isophotes. 
    Finally, we extract a 1-D surface brightness profile along the major axis using 
    the mean ellipticity and position angle. 
    We correct these surface brightness profiles for Galactic extinction and 
    cosmological dimming, and integrate them to various radii to get the luminosity 
    within different physical (elliptical) apertures. 
    Fig~\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z\sim0.2$ and also highlights 
    a few isophotes.

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $>28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to the uncertainty in the background subtraction. 
    We choose to limit our study to surface brightness levels up to $\sim 28.5$ \sb. 
    This is a conservative choice but already enables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    For more details about the technical details of how we use \texttt{Ellipse}, 
    please see Appendix~\ref{app:ellipse}.

    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method. 
    It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    \nbcg{} sample. 
    It is worth noting that this excludes most major-merging massive galaxies. 
%% ------------------------------------------------------------------------------------ %%

@@

    To convert luminosities into stellar mass, we assume that these massive galaxies 
    can be well described by an average \m2l{}. 
    This is a reasonable assumption considering that they are mostly dominated by 
    old stellar populations and are known to have shallow color gradients. 
    We will further justify this point by measuring their median color profiles in 
    Section \ref{ssec:ell_color}.

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    Although \cmodel{} tends to underestimate the total flux for bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipeInPrep}).

    \texttt{iSEDFit} takes a simplified Bayesian approach. 
    In short, it first generates a large grid of SEDs from synthetic stellar population 
    models by drawing randomly from the prior distributions of relevant parameters 
    (e.g. age, metallicity, dust extinction, and star formation history).
    Based on these models, it uses the observed photometry and redshift to compute the 
    statistical likelihood, and generates the posterior probability distribution 
    functions (PDF) for each parameter.  
    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
    full PDF over all the other nuisance parameters.
    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
    marginalized PDF. 
    Please refer to \citet{Moustakas13} for technical details.

@@

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but does
    not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    Based on tests using synthetic objects, we find that the average accuracy of
    \cmodel{} for bright galaxy is roughly at the 1\% level in the $r$, $i$, $z$ bands, 
    and slightly worse in the $g$ and Y-band. 
    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$Y bands (on average, 
    images in $gY$ bands are shallower in depth and/or have higher background noise).  
    The typical uncertainty of \logms{} is around 0.08-0.10 dex at \logms$\sim 11.5$. 
    Please see Appendix~\ref{app:sed} for further details.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/average_mass_profiles_fsps1_A}
      \caption{
          \textbf{Left}: Median \mden{} profiles in three total stellar mass bins. 
              Here we combine the two \rbcg{} and \nbcg{} samples together -- 
              the halo mass dependence of these profiles will be explored in subsequent 
              figures. 
              Thin grey lines show a random subset of individual profiles. 
              The shaded region highlights the region that could be affected by the PSF. 
              Two vertical lines indicate 10 kpc (thin, dotted line) and
              100 kpc (thick, dash line). ~~~ 
          \textbf{Right}: comparison between our \mden{} profiles, previous observations, 
              and simulations. 
              The solid cyan line shows the median profile of massive elliptical 
              galaxies at $z\sim 0$ from \citet[][]{Huang2013a}. 
              The red long-dashed line shows the median profile of massive galaxies at 
              $0.25 \leq z < 0.50$ observed by \textit{HST} from \citet[][]{Patel2013}. 
              The purple short-dashed line shows the median radial stellar distributions 
              in massive halos from simulation using the particle tagging method
              (\citealt{Cooper13}).}
      \label{fig:avg_prof}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          \mden{} profiles for \mtot{}-matched ($11.6<$\logmtot{}$<11.9$) and 
          \minn{}-matched ($11.2<$\logminn{}$<11.6$) samples. 
          Orange and red correspond to \rbcg{} and grey and black correspond to \nbcg{}. 
          The \mtot{}-matched samples are shown on the left and the \minn{}-matched 
          samples are shown on the right. 
          Thin lines show the \mden{} profile for individual galaxies. 
          Thick lines with shaded regions show the median profile for each sample with 
          uncertainties given by the shaded region. 
          The bottom panel highlights the differences between the two median profiles 
          (brown solid line and shaded region). 
          To test the significance of the differential profile, we perform statistical
          tests by comparing the median profiles of two random groups that are drawn 
          from the mixed sample, and have the same sizes with the matched \rbcg{} and
          \nbcg{} ones. 
          Repeating this process 5000 times, the median (black solid line), 1-$\sigma$ 
          (dark-grey shaded region) and 3-$\sigma$ (light-grey shaded region) ranges
          of these random differential profiles are shown on the bottom panel.}
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%     
    \subsection{Impact of Missing Light on the Galaxy Stellar Mass Function}
    \label{ssec:s82}
